--- 
# Change YAML Header
title: "Day6: RMarkdown Practice"
author: "Nithisha"
date: "`r Sys.Date()`" #dynamic date
output: 
  # html_document: 
    slidy_presentation:
    toc: true # table of content
    toc_float: true # float 
---

# 1.About the Challenge Expo

The Annual Data Challenge Expo is jointly sponsored by three American Statistical Association (ASA) Sections – Statistical Computing, Statistical Graphics, and Government Statistics.

## 1.1 Data
<!-- Turn the line that begins with "Data" into a second level header.-->

<!-- Change the words atmos and nasaweather into a monospaced font suitable for code snippets. (backticks)-->

<!-- Make the letter R italicized. (astictic)-->

<!-- Change "ASA Data Expo" to a link that points to https://community.amstat.org/dataexpo/home.-->
The `atmos` data set resides in the `nasaweather` package of the *R* programming language. It contains a collection of atmospheric variables measured between 1995 and 2000 on a grid of 576 coordinates in the western hemisphere. The data set comes from the [ASA Data Expo](https://community.amstat.org/dataexpo/home).


<!-- Turn the above text into a bulleted list with 3 bullets:  temp, pressure, ozone.-->

<!-- Make temp, pressure, ozone bold at the start of each entry.-->

<!-- Make K, mb, and DU italicized at the end of each entry.-->
Some of the variables in the atmos data set are:

+ **Temp** - The mean monthly air temperature near the surface of the Earth (measured in degrees kelvin (_K_))
+ **Pressure** - The mean monthly air pressure at the surface of the Earth (measured in millibars (_mb_))
+ **Ozone** - The mean monthly abundance of atmospheric ozone (measured in Dobson units (_DU_))


<!-- Insert the conversion formula celsius = kelvin – 273.15 here and display it on a separate row -->
You can convert the temperature unit from Kelvin to Celsius with the formula 
$$ celsius = kelvin – 273.15 $$

And you can convert the result to Fahrenheit with the formula

$$ fahrenheit = celsius \times \frac{9}{5} + 32 $$

## 1.2 Preparing the Data

To analyze this data, we will use the following R packages: library(nasaweather) and library(tidyverse)

<!-- Set message=FALSE so messages are not produced in your report when you load the packages-->

<!-- Insert code chunk 1 here -->
```{r message=FALSE, warning=FALSE}
library(nasaweather)
library(tidyverse)
```

For the remainder of the report, we will look only at data from the year 1995 . We aggregate our data by location, using the *R* code below.

<!-- Insert code chunk 2 here -->
```{r message=FALSE, warning=FALSE}
means <- atmos %>%
  filter(year == year) %>%
  group_by(long, lat) %>%
  summarize(temp = mean(temp, na.rm = TRUE),
            pressure = mean(pressure, na.rm = TRUE),
            ozone = mean(ozone, na.rm = TRUE),
            cloudlow = mean(cloudlow, na.rm = TRUE),
            cloudmid = mean(cloudmid, na.rm = TRUE),
            cloudhigh = mean(cloudhigh, na.rm = TRUE)) %>%
  ungroup()
```

## 1.3 Ozone and temperature

Is the relationship between ozone and temperature useful for understanding fluctuations in ozone? A scatterplot of the variables shows a strong, but unusual relationship.

<!-- Insert code chunk 3 here -->

<!-- Set the code chunk options: echo = FALSE, fig.height = 4, fig.width = 5, fig.align = "center"-->

```{r message=FALSE, warning=FALSE, echo = FALSE, fig.height = 4, fig.width = 5, fig.align = "center"}
ggplot(data = means, aes(x = temp, y = ozone)) + geom_point()
```

We suspect that group level effects are caused by environmental conditions that vary by locale. To test this idea, we sort each data point into one of four geographic regions:

<!-- Insert code chunk 4 here -->
```{r Region}
means$locale <- "north america"
means$locale[means$lat < 10] <- "south pacific"
means$locale[means$long > -80 & means$lat < 10] <- "south america"
means$locale[means$long > -80 & means$lat > 10] <- "north atlantic"
```

# 2. Conclusions

We suggest that ozone is highly correlated with temperature, but that a different relationship exists for each geographic region
